### 2020-03-21 korea.tex
update

\begin{flushleft}{
	\Large
	\textbf\newline{
		Estimating the effects of social distancing on preventing the spread of coronavirus disease 2019 (COVID-19) in South Korea
	}
}
\end{flushleft}

@@

Here, we use traffic data to compare and contrast the potential role of social distancing in preventing the spread of COVID-19 in two geographically separated major cities in South Korea.

@@

Here, we analyze epidemiological data, collected bewteen January 20--March 16, 2020, describing the COVID-19 outbreak in Korea.
Daily number of reported cases in each geographic region was transcribed from press releases by Korea Centers for Disease Control and Prevention (KCDC).
Partial line lists were transcribed from press releases and reports from KCDC and various local and provincial government websites.
All data and original reports are stored in a publicly available GitHub repoository: https://github.com/parksw3/COVID19-Korea.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figure_compare_report.pdf}
\caption{
\textbf{Comparison of epidemiological and traffic data from Daegu and Seoul.}
Solid lines represent the daily metro traffic volume in 2020 (red) and in 2017--2019 (gray).
Black lines represent the average daily metro traffic volume in previous years.
}
\label{fig:data}
\end{figure}

We focus our analysis on two cities in which the biggest number of COVID-19 cases have been reported: Daegu and Seoul.
Bewteen January 20--March 16, 2020, 6,083 cases were reported from Daegu and 248 from Seoul.
Need one or two sentences about epidemic.

Daily metro traffic from Daegu and Seoul were obtained from their corresponding government websites.
Need one or two sentences about metro. 
About 80\% decrease in Daegu and 50\% decrease in Seoul after the identification of the church-related case.

@@

We first estimate the time-varying effective reproduction number $R_t$ for both epidemics.
We account for changes in case definition by scaling the number of reported cases by the relative detection rate (i.e., a proportion of cases tested positive based a case definition divided by the mean detection rate among case definitions); 
using a narrow case definition is more likely to have a higher detection rate and a lower reporting rate than a wide one.
Likewise, we account for changes in the number of tests by scaling the number of reported cases again by the relative number of tests performed on each day; this step is performed separately for each case definition because the widening of a case definition necessarily increases the number of tests.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_traffic_regression.pdf}
\caption{
\textbf{Relationship between daily traffic volume and effective reproduction number.}
}
\label{fig:traffic}
\end{figure}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_all.pdf}
\caption{
\textbf{Comparison of effective reproduction number in Daegu, Seoul, Gyeongsangbuk-do, and Gyeonggi-do.}
}
\label{fig:eff}
\end{figure}

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Potential roles of social distancing in preventing the spread of coronavirus disease 2019 (COVID-19) in South Korea
	}
}
\end{flushleft}

@@

Since its appearance in December 2019, the novel coronavirus disease (COVID-19) has spread internationally, including to South Korea.
The first COVID-19 case in South Korea was confirmed on January 20, 2020, from a traveling resident of Wuhan, China.
The epidemic took off in mid-February when COVID-19 began to spread within a church from a city of Daegu --- as of March 18, 2020, 8,413 cases have been confirmed, of which 60\% are linked to the church.
Despite the lack of draconian measures such as in China, the epidemic has been subsiding in South Korea.
Its success in controlling the spread has been widely attributed to its intensive testing.
Here, we describe potential roles of social distancing in mitigating the spread of COVID-19 by comparing epidemics in two geographically separated major cities in South Korea.

@@

We analyze epidemiological data, collected bewteen January 20--March 16, 2020, describing the COVID-19 outbreak in Korea.
Daily number of reported cases in each geographic region was transcribed from press releases by \cite{kcdc}.
Partial line lists were transcribed from press releases and reports from KCDC and various local and provincial government websites.
All data, sources, and original reports are stored in a publicly available GitHub repoository: \url{https://github.com/parksw3/COVID19-Korea}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figure_compare_report.pdf}
\caption{
\textbf{Comparison of epidemiological and traffic data from Daegu and Seoul.}
Red lines represent the daily metro traffic volume in 2020.
Black lines represent the average daily metro traffic volume in previous years, 2017--2019.
Daily traffic from previous years have been shifted by 1--3 days to align day of the week.
}
\label{fig:data}
\end{figure}

We compare epidemiological dynamics of COVID-19 from two cities in which the biggest number of COVID-19 cases have been reported: Daegu and Seoul.
% population size: 2.4 and 9.7 million \citep{kosis}.
Bewteen January 20--March 16, 2020, 6,083 cases were reported from Daegu and 248 from Seoul.
Unlike the epidemic in Daegu, which is characterized by a single, large peak followed by a persistent decrease, the epidemic in Seoul consists of several small outbreaks (\fref{data}).

Daily metro traffic in Daegu and Seoul between 2017--2020 was obtained from their corresponding government websites.

\fref{data}
About 80\% decrease in Daegu and 50\% decrease in Seoul after the identification of the church-related case.

@@

We estimate the time-varying effective reproduction number $R_t$ for both epidemics.
We account for changes in case definition by scaling the number of reported cases by the relative detection rate (i.e., a proportion of cases tested positive based a case definition divided by the mean detection rate among case definitions); 
using a narrow case definition is more likely to have a higher detection rate and a lower reporting rate than a wide one.
Likewise, we account for changes in the number of tests by scaling the number of reported cases again by the relative number of tests performed on each day; this step is performed separately for each case definition because the widening of a case definition necessarily increases the number of tests.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_traffic_regression.pdf}
\caption{
\textbf{Other effects.}
}
\label{fig:traffic}
\end{figure}

@@

\bibliography{korea}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_all.pdf}
\caption{
\textbf{Comparison of effective reproduction number in Daegu, Seoul, Gyeongsangbuk-do, and Gyeonggi-do.}
}
\end{figure}
